A simulation model of DNA methylation data

### 2015-04-06 Rmarkdown/methsim.Rmd
Begin methsim results section

-  __TODO: Figure showing 'rest of genome' is MMRs. More generally, a figure showing the average methylation level in each of `UMR`, `LMR`, `PMR` and `other`.

\subsection{Case study}

>>>>

-  __TODO: Figure showing 'rest of genome' is MMRs. More generally, a figure showing the average methylation level in each of `UMR`, `LMR`, `PMR` and `other`.
- [ ] DONE

A central pillar of `methsim` is that many of the simulation parameters are sampled from real data. At a bare minimum, the first test of `methsim` is that simulated data are similar to the real data on which they are based. To assess this, I compare several summary measures between the simulated data and the real data. The simplest of these are summaries are the distributions of $\beta$-values and within-fragment co-methylation, which are explicitly sampled in `methsim`. In contrast, the spatial correlation of $\beta$-values is not explicitly modelled in `methsim`; rather, we hope that `methsim` recapitulates this phenomenon by appropriate modelling of within-fragment co-methylation and choice of weights, $\mathbf{W}$.

Once it is established that `methsim` passes this minimal test, I use `methsim` to explore models of within-fragment co-methylation, the choice of the weights, $\mathbf{W}$, and their respective effects on the summary measures in order to identify areas of improvement in `methsim`. Finally, I demonstrate how `methsim` might be used to simulate data for use in a study comparing methods for identifying differential methylation.

\subsection{Summary measures of simulated data}

\subsection{Models of within-fragment co-methylation}

\subsection{The choice of $\mathbf{W}$}

\subsection{Simulating differential methylation}
